|

### 2018-10-18 Paper.Rmd
More testing with Erin's suggestions

>>>>

```{r panel effects mmodeling, eval=T}
# Maybe helpful https://onlinecourses.science.psu.edu/stat502/node/162/
# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf 
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")
```
